\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics.tex
npa done

  \item Skedge’s \emph{navigations-per-add} demonstrate its \textbf{effectiveness} in the user search paradigms of \textbf{a) direct search} and \textbf{b) exploratory search}.

>>>>

  \item Skedge’s \emph{navigations-per-add} demonstrate its \textbf{effectiveness} in the user search paradigms of \textbf{a) direct search}, \textbf{b) exploratory search}, and \textbf{c) peer-guided search}.

### 2016-04-13 analytics/npa.tex
npa done

  :(

>>>>

  Given more time with Skedge Social being live and more forethought in tracking its usage, similar data analysis could be done on the subject of the effectiveness of Skedge in peer-guided course finding. Unfortunately, usage data to answer questions such as ``how many Facebook friends were listed as liking or taking a course when it was added?'', and cannot be recreated due to Skedge's purposeful privacy limitations (Facebook friend data can only be retrieved client-side---no data is stored on the server that could authorize such a data request). Thus, part (c) of hypothesis \#2 cannot be verified.

### 2016-04-13 paper.tex
npa done

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the two major use-cases associated with course scheduling---direct and exploratory search---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

>>>>

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the three major use-cases associated with course scheduling---direct, exploratory, and peer-guided search---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.
